# Adding interaction

The `bookdown` format is compatible with many JavaScript-based packages such as `shiny` and `plotly`. This means that we can create books where users can interact with graphs, dashboards, and more!

In this section we focus on `reactable`, a package that allows users to interactively sort and filter tables, similarly to an Excel workbook. 

`kable` is the default package used to render tables in `bookdown`. Here is an example we might use in dataset documentation:

```{r,echo=F}
kable2(
  t1, 
  caption = "Students with disabilities",
) %>%
  column_width(c(1,4)) %>%
  column_width(3, width = medium)
```

`reactable` is a package in R that uses JavaScript to allow us Excel-like interactivity in codebook documentation. We get the best of both worlds: this is integrated directly into the text, allowing additional notation, and we can also filter, sort, and search long documentation for the variables we are interested in. Here is a working example:

```{r, echo=FALSE, warning=FALSE}
reactable2(codebook,
           columns=list(
             Description=colDef(minWidth=120),
             Values=colDef(minWidth=80)
           ))
```
